Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-09 sections/correlated-sicm-and-fm.tex

>>>>

%work in progress / noch nicht fertig
Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a combination of SICM and confocal 
microscopy tracking the sample surface. This combination enables simultaneous SICM and FM imaging of
the same region, in this case the surface, of the same sample at the same time. To achieve matching
field of views, pixel sizes and recording times consequentially yielding two correlating data sets,
two slightly different setups are imaginable and have been put to the test (see figure 
\ref{fig:sicm+sscm_setup}) \cite{Gorelik2002}\cite{Shevchuk2013}.
\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+sscm_setup}
  \caption{%
    \textbf{Two possible setups for a combined SIC and SSC microscope.}
    \textbf{a: Diagram of the combined setup with a xyz sample scan.}
    \textbf{b: Diagram of the combined setup with a xy sample scan and a z probe scan.} 
    Reprinted with permission from ref \cite{Shevchuk2013}.
  }
  \label{fig:sicm+sscm_setup}
\end{figure}
